Deep Probabilistic Models for Camera Geo-Calibration

### 2018-08-13 chapters/introduction/introduction.tex
add time estimation related work

For many applications, knowing when, where, and in which direction a
picture was taken is important to understand the world. We refer to 
estimating these properties as the task of  {\em geo-calibration}.
In current work of geo-calibration, most algorithms are
deterministic, which means they output fixed solutions. Deterministic
systems may seem straight-forward but they also have some obvious
drawbacks: 1) Deterministic systems can not model the inherent
uncertainties from images of ambiguous scenes. 2) They are not
friendly to applications that take probabilistic inputs. To address
these problems, We propose to build probabilistic models for camera
geo-calibration.

@@

Extracting location-dependent or orientation-dependent features from
image data has drawn a great detail of attention from the vision
community~\cite{jacobs07geolocate, jacobs11geolocate,
jacobs08geoorient}. The common trend amongst these methods is that
they take advantage of a large dataset of geo-referenced images. Hays
and Efros~\cite{hays2008im2gps} use a data-driven scene matching
approach to localize a query image using a large dataset of geo-tagged
images.  Doersch et al. extract location-dependent features that
capture the relative appearance differences of large cities.  Lin et
al.~\cite{lin2013cross} localize a ground-level image by learning the
relationship between pairs of ground and aerial images of the same
location. Other techniques focus on urban environments and infer
location using local image
descriptors~\cite{schindler2008detecting,snavely2006photo}. Li et
al.~\cite{li2012worldwide} exploit geo-registered 3D points clouds to
estimate camera pose. Many other cues exist, such as the
skyline~\cite{baatz2012large,ramalingam2009geolocalization}, sky
appearance~\cite{lalonde2010sun,workman2014rainbow}, and
shadows~\cite{junejo2008estimating,wu2010geo}.

@@

\subsection{Deep Neural Networks for Geo-Calibration}
In recent years, deep neural networks (DNNs) were proven to be
extremely successful in many computer vision areas (\todo{citations}). 
The deep neural networks prove to be a good tool to extract high-level
image representations, this valuable ability offers great help for researchers
to conquer the problems like geo-localization and camera calibration.
Recent work on cross-view image
geo-localization~\cite{lin2013cross,lin2015learning,workman2015geocnn,workman2015wide}
has shown that convolutional neural networks are capable of extracting
features from geo-tagged aerial imagery that can be matched to features extracted
from the inquiry ground imagery.  Vo \etal~\cite{vo2016localizing} extend this
line of work, demonstrating improved geo-localization performance by
applying an auxiliary loss function to regress the ground-level camera
orientation with respect to the aerial image.

>>>>

For many applications, knowing when, where, and in which direction a
picture was taken is important to understand the world. We refer to 
estimating these properties as the task of  {\em geo-calibration}.
In current work of geo-calibration, a lot of them are
deterministic, which means they output fixed solutions. Deterministic
systems may seem straight-forward but they also have some obvious
drawbacks: 1) Deterministic systems can not model the inherent
uncertainties from images of ambiguous scenes. 2) They are not
friendly to applications that take probabilistic inputs. To address
these problems, We propose to build probabilistic models for camera
geo-calibration.

@@

Extracting location-dependent or orientation-dependent features from
image data has drawn a great detail of attention from the vision
community~\cite{jacobs07geolocate, jacobs11geolocate,
jacobs08geoorient}. The common trend amongst these methods is that
they take advantage of a large dataset of geo-referenced images. Hays
and Efros~\cite{hays2008im2gps} use a data-driven scene matching
approach to localize a query image using a large dataset of geo-tagged
images.  Doersch et al. extract location-dependent features that
capture the relative appearance differences of large cities.  Lin et
al.~\cite{lin2013cross} localize a ground-level image by learning the
relationship between pairs of ground and aerial images of the same
location. Other techniques focus on urban environments and infer
location using local image
descriptors~\cite{schindler2008detecting,snavely2006photo}. Li et
al.~\cite{li2012worldwide} exploit geo-registered 3D points clouds to
estimate camera pose. Many other cues exist, such as the
skyline~\cite{baatz2012large,ramalingam2009geolocalization}, sky
appearance~\cite{lalonde2010sun,workman2014rainbow}, and
shadows~\cite{junejo2008estimating,wu2010geo}.
For time estimation, Matzen and Snavely~\cite{matzen2014scene} predict
timestamps for photos by matching against a time-varying
reconstruction of a scene.  Hill~\cite{hill1994elephant} estimate the
time of the day by analyze the light intensity profiles captured by
cameras.

@@

\subsection{Deep Learning in Geo-Calibration}
In recent years, deep neural networks (DNNs) were proven to be
extremely successful in many computer vision areas (\todo{citations}). 
The deep neural networks prove to be a good tool to extract high-level
image representations, this valuable ability offers great help for researchers
to conquer the problems like geo-localization and camera calibration.
Recent work on cross-view image
geo-localization~\cite{lin2013cross,lin2015learning,workman2015geocnn,workman2015wide}
has shown that convolutional neural networks are capable of extracting
features from geo-tagged aerial imagery that can be matched to features extracted
from the inquiry ground imagery.  Vo \etal~\cite{vo2016localizing} extend this
line of work, demonstrating improved geo-localization performance by
applying an auxiliary loss function to regress the ground-level camera
orientation with respect to the aerial image.
